---
title: "Casco Claims: Branches and Interactions 2019 UPDATE"
author: "János Poór"
date: "`r Sys.Date()`"
output: rmdformats::readthedown
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r, message = FALSE, echo = TRUE, include = FALSE}
library(config)
library(dplyr)
library(ggplot2)
library(purrr)
library(lubridate)
library(gridExtra)
library(tidyr)
library(scales)
library(stringr)
```


```{r, include=FALSE}
# Data Extraction #######################################################################

# Set JAVA_HOME, set max. memory, and load rJava library
Sys.setenv(JAVA_HOME = "C:\\Program Files\\Java\\jre1.8.0_171")
options(java.parameters = "-Xmx2g")
library(rJava)

# Output Java version
.jinit()
print(.jcall("java/lang/System", "S", "getProperty", "java.version"))

# Load RJDBC library
library(RJDBC)

# Get credentials
datamnr <-
  config::get("datamnr", file = "C:\\Users\\PoorJ\\Projects\\config.yml")

# Create connection driver
jdbcDriver <-
  JDBC(driverClass = "oracle.jdbc.OracleDriver", classPath = "C:\\Users\\PoorJ\\Desktop\\ojdbc7.jar")

# Open connection: kontakt
jdbcConnection <-
  dbConnect(
    jdbcDriver,
    url = datamnr$server,
    user = datamnr$uid,
    password = datamnr$pwd
  )

# Fetch data
query_branches <- "SELECT * FROM T_CLAIMS_MILESTONES_2019"
t_branches <- dbGetQuery(jdbcConnection, query_branches)

query_cutpoints <- "SELECT * FROM T_CLAIMS_MILESTONES_2019_CLEANED"
t_cutpoints <- dbGetQuery(jdbcConnection, query_cutpoints)

query_eventlog <-
"SELECT * FROM T_CLAIMS_PA_OUTPUT_CCC_OKK_2019 a WHERE milestones IS NOT NULL
AND EXISTS (SELECT 1 FROM T_CLAIMS_MILESTONES_2019_CLEANED b WHERE a.case_id = b.case_id)"
t_eventlog <- dbGetQuery(jdbcConnection, query_eventlog)


# Close db connection: kontakt
dbDisconnect(jdbcConnection)


# Transform data
t_eventlog <- t_eventlog %>% mutate_at(vars(EVENT_END), ymd_hms)

t_branches <- t_branches %>% mutate_at(vars(CLAIM_REPORT_DATE, CLAIM_DECISION_DATE, CLAIM_CLOSE_DATE), ymd_hms)
```

# 1. TL;DR

Outline of the main conclusions of the analysis of Casco claims process branches and interactions:  

* Process branches  
	+ Proportion of alternative (STP) claim management is minimal
	+ Proporiton of standard (happyflow) and exception (pending) flow is about 50-50%
* Interactions  
	+ Contact Center: less than 50% of cases have Contact Center interactions
	+ Those cases that have Contact Center interactions have on average 4
	+ **UPDATE 2019** Number of Claims Handling interactions are slightly dropping  
	    - 2017: 17, 2018: 15, 2019: 14
	    - In 2019 11 out of the 14 interactions are done by claim handling experts (rest by logistics or other depts)
	+ Exception flow has most interactions
* Lifecycles  
	+ Most interactions happen between report date and closing date of claim irrespective of process branch
	+ 30% of calls happen in exception flow between report date and closing date of claim  
	    - Customers are most likely to call in between 5-50 days when their claim enters a pending status
	+ 50% of Claim Handling interactions between report date and closing date of claim
	
***	

# 2. Overview of Casco Claims

## 2.1. Monthly Volume and Throughput Time of Closed Casco Claims

Dataset contains 18K reported and closed Casco claims that arrived between 2017/01 and 2019/03. Volume and throughput computations are done for the Jul 2017 - Mar 2019 period to correct for pending cases at the begining and end of the timeline. Monthly fluctuation reflects seasonal peaks in summer months.

```{r, message=FALSE}
p1 <- t_branches %>%
  filter(CLAIM_CLOSE_DATE >= as.Date("2017-07-01") & CLAIM_CLOSE_DATE < as.Date("2019-04-01")) %>%
  mutate(CLAIM_CLOSE_MONTH = lubridate::floor_date(CLAIM_CLOSE_DATE, unit = "month")) %>%
  group_by(CLAIM_CLOSE_MONTH) %>%
  summarize(COUNT_REPORTED_CLAIMS = n()) %>%
  ungroup() %>%
  ggplot(aes(x = CLAIM_CLOSE_MONTH, y = COUNT_REPORTED_CLAIMS)) +
  geom_line() +
  labs(
    x = "Month",
    y = "# of Closed Casco Claims",
    title = "Number of Closed Casco Claims per Month"
  )

p2 <- t_branches %>%
  filter(CLAIM_CLOSE_DATE >= as.Date("2017-07-01") & CLAIM_CLOSE_DATE < as.Date("2019-04-01")) %>%
  mutate(
    CLAIM_CLOSE_MONTH = lubridate::floor_date(CLAIM_CLOSE_DATE, unit = "month"),
    THROUGHPUT_TIME = difftime(CLAIM_CLOSE_DATE, CLAIM_REPORT_DATE, units = "days")
  ) %>%
  group_by(CLAIM_CLOSE_MONTH) %>%
  summarize(AVG_THROUGHPUT = mean(THROUGHPUT_TIME)) %>%
  ungroup() %>%
  ggplot(aes(x = CLAIM_CLOSE_MONTH, y = AVG_THROUGHPUT)) +
  geom_line() +
  labs(
    x = "Month",
    y = "Throughput Time (days)",
    title = "Throughput Time of Closed Casco Claims per Month"
  )

grid.arrange(p1, p2, nrow = 2)
```


## 2.2. Monthly Volume and Throughput Time By Process Branch

Process has three main branches:  

* Alternative: claim management on the phone without survey  
* Standard: claim management with survey without pending states (happyflow)   
* Exception: claim management with survey with pending states

```{r, message=FALSE}
p3 <- t_branches %>%
  filter(CLAIM_CLOSE_DATE >= as.Date("2017-07-01") & CLAIM_CLOSE_DATE < as.Date("2019-04-01")) %>%
  mutate(CLAIM_CLOSE_MONTH = lubridate::floor_date(CLAIM_CLOSE_DATE, unit = "month")) %>%
  group_by(CLAIM_CLOSE_MONTH, CASE_TYPE) %>%
  summarize(COUNT_REPORTED_CLAIMS = n()) %>%
  ungroup() %>%
  mutate(CASE_TYPE = factor(CASE_TYPE, levels=c('ALTERNATIVE','STANDARD','EXCEPTION'))) %>% 
  ggplot(aes(x = CLAIM_CLOSE_MONTH, y = COUNT_REPORTED_CLAIMS)) +
  geom_line() +
  theme(axis.text.x = element_text(angle = 90)) +
  facet_wrap(~ CASE_TYPE) +
  labs(
    x = "Month",
    y = "# of Closed Casco Claims",
    title = "Number of Closed Casco Claims per Month"
  )

p4 <- t_branches %>%
  filter(CLAIM_CLOSE_DATE >= as.Date("2017-07-01") & CLAIM_CLOSE_DATE < as.Date("2019-04-01")) %>%
  mutate(
    CLAIM_CLOSE_MONTH = lubridate::floor_date(CLAIM_CLOSE_DATE, unit = "month"),
    THROUGHPUT_TIME = difftime(CLAIM_CLOSE_DATE, CLAIM_REPORT_DATE, units = "days")
  ) %>%
  group_by(CLAIM_CLOSE_MONTH, CASE_TYPE) %>%
  summarize(AVG_THROUGHPUT = mean(THROUGHPUT_TIME)) %>%
  ungroup() %>%
  mutate(CASE_TYPE = factor(CASE_TYPE, levels=c('ALTERNATIVE','STANDARD','EXCEPTION'))) %>% 
  ggplot(aes(x = CLAIM_CLOSE_MONTH, y = AVG_THROUGHPUT)) +
  geom_line() +
  theme(axis.text.x = element_text(angle = 90)) +
  facet_wrap(~ CASE_TYPE) +
  labs(
    x = "Month",
    y = "Throughput Time (days)",
    title = "Throughput Time of Closed Casco Claims per Month"
  )

grid.arrange(p3, p4, nrow = 2)
```

***



# 3. Analysis of Interactions

## 3.1. Average Interactions per Claim File

For both  Contact Center and Claims Handling we can compute how many times operators interacted with the claim file in the workflow system (Kontakt).

Not every claim file has Contact Center interactions. The average number of Contact Center interactions needs to be differentiated:  

* Contact Center General: average across ALL claim files  
* Contact Center Special: average accross ONLY THOSE claim files that had Contact Center interactions

For Claims Handling there is a decreasing trend of the number of average interactions in time.

```{r, message=FALSE}
# Compute interactions per case
t_interaction_counts <- t_eventlog %>%
  group_by(CASE_ID, ACTIVITY_TYPE) %>%
  summarize(COUNT_OF_ACTIVITY = n()) %>%
  ungroup() %>%
  tidyr::spread(key = ACTIVITY_TYPE, value = COUNT_OF_ACTIVITY, fill = 0)

names(t_interaction_counts) <- c("CASE_ID", "FAIRKAR", "KONTAKT_CCC", "KONTAKT_OKK")

# Add interactions to base table

# Define claim files that have CCC interactions
t_ccc_special <- t_branches %>%
  filter(CLAIM_REPORT_DATE < as.Date("2019-04-01")) %>%
  mutate(CLAIM_REPORT_MONTH = lubridate::floor_date(CLAIM_REPORT_DATE, unit = "month")) %>%
  left_join(t_interaction_counts, by = c("CASE_ID")) %>%
  filter(KONTAKT_CCC != 0) %>% 
  group_by(CLAIM_REPORT_MONTH) %>%
  summarize(
    ContactCenterSpecial = mean(KONTAKT_CCC, na.rm = TRUE))

# Define interactions across all claim files
t_branches %>%
  filter(CLAIM_REPORT_DATE < as.Date("2019-04-01")) %>%
  mutate(CLAIM_REPORT_MONTH = lubridate::floor_date(CLAIM_REPORT_DATE, unit = "month")) %>%
  left_join(t_interaction_counts, by = c("CASE_ID")) %>%
  group_by(CLAIM_REPORT_MONTH) %>%
  summarize(
    ContactCenterGeneral = mean(KONTAKT_CCC, na.rm = TRUE),
    ClaimsHandling = mean(KONTAKT_OKK, na.rm = TRUE)
  ) %>%
  ungroup() %>%
  left_join(t_ccc_special, by = c("CLAIM_REPORT_MONTH")) %>%
  tidyr::gather(-CLAIM_REPORT_MONTH, key = ORG, value = AVG_INT) %>% 
  ggplot(aes(x = CLAIM_REPORT_MONTH, y = AVG_INT)) +
    geom_line() +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_grid(.~ORG) +
    labs(
      x = "Month",
      y = "# of Interactions per Claim File",
      title = "Number of Average Interactions per Claim File"
    )
```


## 3.2. Average Interactions per Claim File By Process Branch

Breakdowns by process branch show that the decreasing trend of average interaction number per claim file in Claims Handling is due to the exception flow.

```{r, message=FALSE}
# Define claim files that have CCC interactions
t_ccc_special_by_case_type <- t_branches %>%
  filter(CLAIM_REPORT_DATE < as.Date("2019-04-01")) %>%
  mutate(CLAIM_REPORT_MONTH = lubridate::floor_date(CLAIM_REPORT_DATE, unit = "month")) %>%
  left_join(t_interaction_counts, by = c("CASE_ID")) %>%
  filter(KONTAKT_CCC != 0) %>%
  mutate(CASE_TYPE = factor(CASE_TYPE, levels=c('ALTERNATIVE','STANDARD','EXCEPTION'))) %>% 
  group_by(CLAIM_REPORT_MONTH, CASE_TYPE) %>%
  summarize(
    ContactCenterSpecial = mean(KONTAKT_CCC, na.rm = TRUE))


# Add interactions to base table
t_branches %>%
  filter(CLAIM_REPORT_DATE < as.Date("2019-04-01")) %>%
  mutate(CLAIM_REPORT_MONTH = lubridate::floor_date(CLAIM_REPORT_DATE, unit = "month")) %>%
  left_join(t_interaction_counts, by = c("CASE_ID")) %>%
  mutate(CASE_TYPE = factor(CASE_TYPE, levels=c('ALTERNATIVE','STANDARD','EXCEPTION'))) %>% 
  group_by(CLAIM_REPORT_MONTH, CASE_TYPE) %>%
  summarize(
    ContactCenter = mean(KONTAKT_CCC, na.rm = TRUE),
    ClaimsHandling = mean(KONTAKT_OKK, na.rm = TRUE)
  ) %>%
  ungroup() %>%
  left_join(t_ccc_special_by_case_type, by = c("CLAIM_REPORT_MONTH", "CASE_TYPE")) %>%
  tidyr::gather(-CLAIM_REPORT_MONTH, -CASE_TYPE, key = ORG, value = AVG_INT) %>% 
  ggplot(aes(x = CLAIM_REPORT_MONTH, -CASE_TYPE, y = AVG_INT)) +
    geom_line() +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_grid(CASE_TYPE~ORG) +
    labs(
      x = "Month",
      y = "# of Interactions per Claim File",
      title = "Number of Average Interactions per Claim File"
    )
```


## 3.3. Breakdown of Claims Handling Interactions by Department

```{r, message=FALSE}
# Compute interactions per case
t_interaction_counts_claimsdept <- t_eventlog %>%
  filter(ACTIVITY_TYPE == "KONTAKT OKK") %>%
  mutate(DEPT = stringr::str_extract(USER_ID, "[^OKK/].*?(?=\\\\)")) %>%
  mutate(DEPT = case_when(
    DEPT == "Gepjarmu/szakertok" ~ "Car/Experts",
    DEPT == "Logisztikai csoport/Levelfeldolgozo" ~ "Logistics/Mailroom",
    TRUE ~ "Other"
  )) %>%
  group_by(CASE_ID, DEPT) %>%
  summarize(COUNT_OF_ACTIVITY = n()) %>%
  ungroup()

# Add interactions to base table
t_branches %>%
  filter(CLAIM_REPORT_DATE < as.Date("2019-04-01")) %>%
  mutate(CLAIM_REPORT_MONTH = lubridate::floor_date(CLAIM_REPORT_DATE, unit = "month")) %>%
  select(CASE_ID, CLAIM_REPORT_MONTH) %>%
  left_join(t_interaction_counts_claimsdept, by = c("CASE_ID")) %>%
  filter(!is.na(DEPT)) %>%
  group_by(CLAIM_REPORT_MONTH, DEPT) %>%
  summarize(AVG_INT = mean(COUNT_OF_ACTIVITY, na.rm = TRUE)) %>%
  ungroup() %>%
  ggplot(aes(x = CLAIM_REPORT_MONTH, y = AVG_INT, group = DEPT, color = DEPT)) +
  geom_line() +
  geom_point() +
  labs(
    x = "Month",
    y = "# of Interactions per Claim File",
    title = "Number of Average Interactions per Claim File\nby Claims Handling Department"
  )
```


## 3.4. Breakdown of Claims Handling Interactions by Department by Process Branch

```{r, message=FALSE}
# Add interactions to base table
t_branches %>%
  filter(CLAIM_REPORT_DATE < as.Date("2019-04-01")) %>%
  mutate(CLAIM_REPORT_MONTH = lubridate::floor_date(CLAIM_REPORT_DATE, unit = "month")) %>%
  select(CASE_ID, CLAIM_REPORT_MONTH, CASE_TYPE) %>% 
  left_join(t_interaction_counts_claimsdept, by = c("CASE_ID")) %>% 
  filter(!is.na(DEPT)) %>% 
  group_by(CLAIM_REPORT_MONTH, DEPT, CASE_TYPE) %>% 
  summarize(AVG_INT = mean(COUNT_OF_ACTIVITY, na.rm = TRUE)) %>% 
  ungroup() %>%
  ggplot(aes(x = CLAIM_REPORT_MONTH, y = AVG_INT, group = DEPT, color = DEPT)) +
  geom_line() +
  geom_point() +
  theme(axis.text.x = element_text(angle = 90)) +
  facet_grid(.~CASE_TYPE) +
  labs(
    x = "Month",
    y = "# of Interactions per Claim File",
    title = "Number of Average Interactions per Claim File\nby Claims Handling Department"
  )
```

***



# 4. Analysis of Claims Lifecycle (2 Cutpoints) Jul 2018 - Apr 2019

Claim file lifecycle can be computed from Fairkar status data. The two major lifecycle cutpoints are:  

* Date of reporting the claim  
* Date of closing the claim file  

The two cutpoints yield five lifecylcle sequences:  

* Before reporting  
* The day of rerporting  
* Between reporting and closing  
* The day of closing  
* After closing  


## 4.1. Contact Center

### 4.1.1. Contact Center Calls across Claims Lifecycle

Breakdown of calls for those claim files that had calls (note: not every claim file has Contact Center interactions, see previous section)

```{r, message=FALSE}
# Define lifecycle cutpoints
t_cutpoints_long <- t_cutpoints %>%
  filter(REPORT_LOWERBOUND >= as.Date("2018-07-01") & REPORT_LOWERBOUND < as.Date("2019-04-01")) %>%
  mutate_at(vars(REPORT_LOWERBOUND:CLOSE_UPPERBOUND), ymd_hms) %>%
  select(-DECISION_LOWERBOUND, -DECISION_UPPERBOUND) %>% 
  tidyr::gather(-CASE_ID, -CASE_TYPE, -MILESTONES, key = CUTPOINT, value = CUTDATE) %>%
  arrange(CASE_ID, CUTPOINT) %>% 
  filter(!is.na(CUTDATE))


# Org specific event seqs
t_events_ccc <- t_eventlog %>%
  filter(
        CASE_ID %in% t_cutpoints_long$CASE_ID &
        ACTIVITY_TYPE == "KONTAKT CCC" &
        ACTIVITY_CHANNEL == "CALL") %>%
  select(CASE_ID, CASE_TYPE, MILESTONES, EVENT_END)


t_events_okk <- t_eventlog %>%
  filter(
        CASE_ID %in% t_cutpoints_long$CASE_ID &
        ACTIVITY_TYPE == "KONTAKT OKK") %>%
  select(CASE_ID, CASE_TYPE, MILESTONES, EVENT_END)

# Define Func to Compute Bins
create_bins_2 <- function(df, case_id) {
  t_cutpoints_long_filtered <- t_cutpoints_long[t_cutpoints_long$CASE_ID == case_id, ] %>% arrange(CUTDATE)
  as.character(cut(df$EVENT_END,
    breaks = c(t_cutpoints_long_filtered$CUTDATE, Inf),
    labels = t_cutpoints_long_filtered$CUTPOINT
  ))
}

# Genereate bins
by_case_id_ccc <- t_events_ccc %>%
  select(-MILESTONES) %>% 
  group_by(CASE_ID, CASE_TYPE) %>%
  nest() %>%
  mutate(BINS = map2(data, .$CASE_ID, ~create_bins_2(df = .x, case_id = .y)))


# Graph
by_case_id_ccc %>% select(CASE_ID, CASE_TYPE, data, BINS) %>% unnest() %>% 
  mutate(
    PERIOD = case_when(
      is.na(BINS) ~ '1_BEFORE_REPORT',
      BINS == 'REPORT_LOWERBOUND' ~ '2_ON_REPORT',
      BINS == 'REPORT_UPPERBOUND' ~ '3_BETWEEN_REPORT_CLOSE',
      BINS == 'CLOSE_LOWERBOUND' ~ '4_ON_CLOSE',
      BINS == 'CLOSE_UPPERBOUND' ~ '5_AFTER_CLOSE'
    )
  ) %>% 
  group_by(PERIOD) %>% 
  summarize(N_OF_CALLS = n()) %>% 
  ungroup() %>% 
  ggplot(aes(x = PERIOD, y = N_OF_CALLS)) +
    geom_bar(stat = "identity") +
    theme(axis.text.x = element_text(angle = 90)) +
    labs(
        x = "Lifecycle",
        y = "# of Calls",
        title = "Number of Calls across Claim File Lifecycle"
      )
```


### 4.1.2. Contact Center Calls across Claims Lifecycle by Process Branch

```{r, message=FALSE}
# Graph
by_case_id_ccc %>% select(CASE_ID, CASE_TYPE, data, BINS) %>% unnest() %>% 
  mutate(
    PERIOD = case_when(
      is.na(BINS) ~ '1_BEFORE_REPORT',
      BINS == 'REPORT_LOWERBOUND' ~ '2_ON_REPORT',
      BINS == 'REPORT_UPPERBOUND' ~ '3_BETWEEN_REPORT_CLOSE',
      BINS == 'CLOSE_LOWERBOUND' ~ '4_ON_CLOSE',
      BINS == 'CLOSE_UPPERBOUND' ~ '5_AFTER_CLOSE'
    )
  ) %>% 
  group_by(PERIOD, CASE_TYPE) %>% 
  summarize(N_OF_CALLS = n()) %>% 
  ungroup() %>% 
  ggplot(aes(x = PERIOD, y = N_OF_CALLS)) +
    geom_bar(stat = "identity") +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_grid(.~CASE_TYPE) +
    labs(
        x = "Lifecycle",
        y = "# of Calls",
        title = "Number of Calls across Claim File Lifecycle by Process Branch"
      )
```


### 4.1.3. Distribution of Calls between Report and Close Dates

Most calls are received between report and closing date. Breaking down this period by days passed after report shows that:

* most calls are received 5 to 10 days after report
* on the exception flow calls keep coming in big volumes until the 50th day

```{r, message=FALSE}
t_calls_ccc <- t_eventlog %>%
  filter(
    CASE_ID %in% t_cutpoints_long$CASE_ID &
      ACTIVITY_TYPE == "KONTAKT CCC" &
      ACTIVITY_CHANNEL == "CALL"
  ) %>%
  select(CASE_ID, MILESTONES, ACTIVITY_EN, EVENT_END)

t_cutpoints %>%
  select(CASE_ID, CASE_TYPE, REPORT_UPPERBOUND, CLOSE_LOWERBOUND) %>%
  mutate(
    CASE_TYPE = factor(CASE_TYPE, levels = c("ALTERNATIVE", "STANDARD", "EXCEPTION")),
    THROUGHPUT_TIME = as.numeric(difftime(CLOSE_LOWERBOUND, REPORT_UPPERBOUND, units = "days")),
    THROUGHPUT_TIME_CAT = cut(THROUGHPUT_TIME, c(seq(0, 90, 15), Inf))
  ) %>%
  inner_join(t_calls_ccc, by = "CASE_ID") %>%
  filter(EVENT_END > REPORT_UPPERBOUND & EVENT_END < CLOSE_LOWERBOUND) %>%
  mutate(
    CALL_DIFF = ceiling(as.numeric(difftime(EVENT_END, REPORT_UPPERBOUND, units = "days"))),
    CALL_DIFF_CAT = cut(CALL_DIFF, c(seq(0, 100, 5), Inf))
  ) %>%
  ggplot(aes(CALL_DIFF)) +
  geom_histogram(bins = 50) +
  coord_cartesian(xlim = c(0, 200)) +
  facet_grid(.~CASE_TYPE) +
  labs(
    x = "Days after report",
    y = "# of Calls",
    title = "Number of Calls after Claim Reporting by Days Passed"
  )
```

Two main call reasons in this period are:  

* Provide information: peaks at 5 days after report
    + Exception flow genereates most provide information calls until approx. 50th day
* Reclamation: peaks at 25 days after report

```{r, message=FALSE}
t_cutpoints %>%
  select(CASE_ID, CASE_TYPE, REPORT_UPPERBOUND, CLOSE_LOWERBOUND) %>%
  mutate(
    CASE_TYPE = factor(CASE_TYPE, levels = c("ALTERNATIVE", "STANDARD", "EXCEPTION")),
    THROUGHPUT_TIME = as.numeric(difftime(CLOSE_LOWERBOUND, REPORT_UPPERBOUND, units = "days")),
    THROUGHPUT_TIME_CAT = cut(THROUGHPUT_TIME, c(seq(0, 90, 15), Inf))
  ) %>%
  inner_join(t_calls_ccc, by = "CASE_ID") %>%
  filter(EVENT_END > REPORT_UPPERBOUND & EVENT_END < CLOSE_LOWERBOUND) %>%
  mutate(
    CALL_DIFF = ceiling(as.numeric(difftime(EVENT_END, REPORT_UPPERBOUND, units = "days"))),
    CALL_DIFF_CAT = cut(CALL_DIFF, c(seq(0, 100, 5), Inf)),
    ACTIVITY_EN = factor(case_when(
      ACTIVITY_EN == "Tajekoztatas" ~ "Provide information",
      ACTIVITY_EN == "Reklamacio  OKK-ba tovabbitva" ~ "Reclamation",
      TRUE ~ "Other"
    ), levels = c("Provide information", "Reclamation", "Other"))
  ) %>%
  ggplot(aes(CALL_DIFF)) +
  geom_histogram(bins = 50) +
  coord_cartesian(xlim = c(0, 200)) +
  facet_grid(CASE_TYPE ~ ACTIVITY_EN) +
  labs(
    x = "Days after report",
    y = "# of Calls",
    title = "Number of Calls after Claim Reporting by Days Passed"
  )
```


## 4.2. Claims Handling

### 4.2.1. Claims Handling Interactions across Claims Lifecycle

```{r, message=FALSE}
# Genereate bins
by_case_id_okk <- t_events_okk %>%
  select(-MILESTONES) %>% 
  group_by(CASE_ID, CASE_TYPE) %>%
  nest() %>%
  mutate(BINS = map2(data, .$CASE_ID, ~create_bins_2(df = .x, case_id = .y)))


# Graph
by_case_id_okk %>% select(CASE_ID, CASE_TYPE, data, BINS) %>% unnest() %>% 
  mutate(
    PERIOD = case_when(
      is.na(BINS) ~ '1_BEFORE_REPORT',
      BINS == 'REPORT_LOWERBOUND' ~ '2_ON_REPORT',
      BINS == 'REPORT_UPPERBOUND' ~ '3_BETWEEN_REPORT_CLOSE',
      BINS == 'CLOSE_LOWERBOUND' ~ '4_ON_CLOSE',
      BINS == 'CLOSE_UPPERBOUND' ~ '5_AFTER_CLOSE'
    )
  ) %>% 
  group_by(PERIOD) %>% 
  summarize(N_OF_CALLS = n()) %>% 
  ungroup() %>% 
  ggplot(aes(x = PERIOD, y = N_OF_CALLS)) +
    geom_bar(stat = "identity") +
    scale_y_continuous(label = unit_format(unit = "K", scale = 1e-3)) +
    theme(axis.text.x = element_text(angle = 90)) +
    labs(
        x = "Lifecycle",
        y = "# of Claims Handling Interactions",
        title = "Number of Claims Handling Interactions across Claim File Lifecycle"
      )
```


### 4.2.2. Claims Handling Interactions across Claims Lifecycle by Process Branch

```{r, message=FALSE}
# Graph
by_case_id_okk %>% select(CASE_ID, CASE_TYPE, data, BINS) %>% unnest() %>% 
  mutate(
    PERIOD = case_when(
      is.na(BINS) ~ '1_BEFORE_REPORT',
      BINS == 'REPORT_LOWERBOUND' ~ '2_ON_REPORT',
      BINS == 'REPORT_UPPERBOUND' ~ '3_BETWEEN_REPORT_CLOSE',
      BINS == 'CLOSE_LOWERBOUND' ~ '4_ON_CLOSE',
      BINS == 'CLOSE_UPPERBOUND' ~ '5_AFTER_CLOSE'
    )
  ) %>% 
  group_by(PERIOD, CASE_TYPE) %>% 
  summarize(N_OF_CALLS = n()) %>% 
  ungroup() %>% 
  ggplot(aes(x = PERIOD, y = N_OF_CALLS)) +
    geom_bar(stat = "identity") +
    scale_y_continuous(label = unit_format(unit = "K", scale = 1e-3)) +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_grid(.~CASE_TYPE) +
    labs(
        x = "Lifecycle",
        y = "# of Claims Handling Interactions",
        title = "Number of Claims Handling Interactions across Claim File Lifecycle \nby Process Branch"
      )
```

### 4.2.3. Distribution of Claims Handling Interactions between Report and Close Dates

Most interactions happen between report and closing date. Breaking down this period by days passed after report shows that:

* most interactions take place 5 to 10 days after report

```{r, message=FALSE}
t_events_okk <- t_eventlog %>%
  filter(
    CASE_ID %in% t_cutpoints_long$CASE_ID &
      ACTIVITY_TYPE == "KONTAKT OKK"
  ) %>%
  select(CASE_ID, MILESTONES, EVENT_END, USER_ID) %>%
  mutate(DEPT = stringr::str_extract(USER_ID, "[^OKK/].*?(?=\\\\)")) %>%
  mutate(DEPT = case_when(
    DEPT == "Gepjarmu/szakertok" ~ "Car/Experts",
    DEPT == "Logisztikai csoport/Levelfeldolgozo" ~ "Logistics/Mailroom",
    TRUE ~ "Other"
  ))

t_cutpoints %>%
  select(CASE_ID, CASE_TYPE, REPORT_UPPERBOUND, CLOSE_LOWERBOUND) %>%
  mutate(
    CASE_TYPE = factor(CASE_TYPE, levels = c("ALTERNATIVE", "STANDARD", "EXCEPTION")),
    THROUGHPUT_TIME = as.numeric(difftime(CLOSE_LOWERBOUND, REPORT_UPPERBOUND, units = "days")),
    THROUGHPUT_TIME_CAT = cut(THROUGHPUT_TIME, c(seq(0, 90, 15), Inf))
  ) %>%
  inner_join(t_events_okk, by = "CASE_ID") %>%
  filter(EVENT_END > REPORT_UPPERBOUND & EVENT_END < CLOSE_LOWERBOUND) %>%
  mutate(
    CALL_DIFF = ceiling(as.numeric(difftime(EVENT_END, REPORT_UPPERBOUND, units = "days"))),
    CALL_DIFF_CAT = cut(CALL_DIFF, c(seq(0, 100, 5), Inf))
  ) %>%
  ggplot(aes(CALL_DIFF)) +
  geom_histogram(bins = 50) +
  coord_cartesian(xlim = c(0, 200)) +
  facet_grid(. ~ CASE_TYPE) +
  labs(
    x = "Days after report",
    y = "# of Calls",
    title = "Number of Interactions after Claim Reporting by Days Passed"
  )
```

There is no difference in peak point between process branches.

```{r, message=FALSE}
t_cutpoints %>%
  select(CASE_ID, CASE_TYPE, REPORT_UPPERBOUND, CLOSE_LOWERBOUND) %>%
  mutate(
    CASE_TYPE = factor(CASE_TYPE, levels = c("ALTERNATIVE", "STANDARD", "EXCEPTION")),
    THROUGHPUT_TIME = as.numeric(difftime(CLOSE_LOWERBOUND, REPORT_UPPERBOUND, units = "days")),
    THROUGHPUT_TIME_CAT = cut(THROUGHPUT_TIME, c(seq(0, 90, 15), Inf))
  ) %>%
  inner_join(t_events_okk, by = "CASE_ID") %>%
  filter(EVENT_END > REPORT_UPPERBOUND & EVENT_END < CLOSE_LOWERBOUND) %>%
  mutate(
    CALL_DIFF = ceiling(as.numeric(difftime(EVENT_END, REPORT_UPPERBOUND, units = "days"))),
    CALL_DIFF_CAT = cut(CALL_DIFF, c(seq(0, 100, 5), Inf))
  ) %>%
  ggplot(aes(CALL_DIFF)) +
  geom_histogram(bins = 50) +
  coord_cartesian(xlim = c(0, 200)) +
  facet_grid(DEPT ~ CASE_TYPE) +
  labs(
    x = "Days after report",
    y = "# of Calls",
    title = "Number of Interactions after Claim Reporting by Days Passed"
  )
```

***


# 5. Analysis of Claims Lifecycle (3 Cutpoints) Jul 2018 - Apr 2019

Claim file lifecycle can be computed from Fairkar status data. The three major lifecycle cutpoints are:  

* Date of reporting the claim
* Date of survey ready
* Date of closing the claim file  

The three cutpoints yield seven lifecylcle sequences:  

* Before reporting  
* The day of rerporting  
* Between reporting and survey ready
* The day of survey ready
* Between survey ready and closing
* The day of closing  
* After closing  


## 5.1. Contact Center

### 5.1.1. Contact Center Calls across Claims Lifecycle

Breakdown of calls for those claim files that had calls (note: not every claim file has Contact Center interactions, see previous section)

```{r, message=FALSE}
# Define lifecycle cutpoints
t_cutpoints_long_3 <- t_cutpoints %>%
  filter(REPORT_LOWERBOUND >= as.Date("2018-07-01") & REPORT_LOWERBOUND < as.Date("2019-04-01")) %>%
  mutate_at(vars(REPORT_LOWERBOUND:CLOSE_UPPERBOUND), ymd_hms) %>%
  filter(!is.na(DECISION_LOWERBOUND)) %>% 
  tidyr::gather(-CASE_ID, -CASE_TYPE, -MILESTONES, key = CUTPOINT, value = CUTDATE) %>%
  arrange(CASE_ID, CUTPOINT) %>% 
  filter(!is.na(CUTDATE))


# Org specific event seqs
t_events_ccc <- t_eventlog %>%
  filter(
        CASE_ID %in% t_cutpoints_long_3$CASE_ID &
        ACTIVITY_TYPE == "KONTAKT CCC" &
        ACTIVITY_CHANNEL == "CALL") %>%
  select(CASE_ID, CASE_TYPE, MILESTONES, EVENT_END)


t_events_okk <- t_eventlog %>%
  filter(
        CASE_ID %in% t_cutpoints_long_3$CASE_ID &
        ACTIVITY_TYPE == "KONTAKT OKK") %>%
  select(CASE_ID, CASE_TYPE, MILESTONES, EVENT_END)


# Define Func to Compute Bins
create_bins_3 <- function(df, case_id) {
  t_cutpoints_long_filtered <- t_cutpoints_long_3[t_cutpoints_long_3$CASE_ID == case_id, ] %>% arrange(CUTDATE)
  as.character(cut(df$EVENT_END,
    breaks = c(t_cutpoints_long_filtered$CUTDATE, Inf),
    labels = t_cutpoints_long_filtered$CUTPOINT
  ))
}

# Genereate bins
by_case_id_ccc_3 <- t_events_ccc %>%
  select(-MILESTONES) %>% 
  group_by(CASE_ID, CASE_TYPE) %>%
  nest() %>%
  mutate(BINS = map2(data, .$CASE_ID, ~create_bins_3(df = .x, case_id = .y)))


# Graph
by_case_id_ccc_3 %>% select(CASE_ID, CASE_TYPE, data, BINS) %>% unnest() %>% 
  mutate(
    PERIOD = case_when(
      is.na(BINS) ~ '1_BEFORE_REPORT',
      BINS == 'REPORT_LOWERBOUND' ~ '2_ON_REPORT',
      BINS == 'REPORT_UPPERBOUND' ~ '3_BETWEEN_REPORT_SURVEYREADY',
      BINS == 'DECISION_LOWERBOUND' ~ '4_ON_SURVEYREADY',
      BINS == 'DECISION_UPPERBOUND' ~ '5_BETWEEN_SURVEYREADY_CLOSE',
      BINS == 'CLOSE_LOWERBOUND' ~ '6_ON_CLOSE',
      BINS == 'CLOSE_UPPERBOUND' ~ '7_AFTER_CLOSE'
    )
  ) %>% 
  group_by(PERIOD) %>% 
  summarize(N_OF_CALLS = n()) %>% 
  ungroup() %>% 
  ggplot(aes(x = PERIOD, y = N_OF_CALLS)) +
    geom_bar(stat = "identity") +
    theme(axis.text.x = element_text(angle = 90)) +
    labs(
        x = "Lifecycle",
        y = "# of Calls",
        title = "Number of Calls across Claim File Lifecycle"
      )
```


### 5.1.2. Contact Center Calls across Claims Lifecycle by Process Branch

```{r, message=FALSE}
# Graph
by_case_id_ccc_3 %>% select(CASE_ID, CASE_TYPE, data, BINS) %>% unnest() %>% 
   mutate(
    PERIOD = case_when(
      is.na(BINS) ~ '1_BEFORE_REPORT',
      BINS == 'REPORT_LOWERBOUND' ~ '2_ON_REPORT',
      BINS == 'REPORT_UPPERBOUND' ~ '3_BETWEEN_REPORT_SURVEYREADY',
      BINS == 'DECISION_LOWERBOUND' ~ '4_ON_SURVEYREADY',
      BINS == 'DECISION_UPPERBOUND' ~ '5_BETWEEN_SURVEYREADY_CLOSE',
      BINS == 'CLOSE_LOWERBOUND' ~ '6_ON_CLOSE',
      BINS == 'CLOSE_UPPERBOUND' ~ '7_AFTER_CLOSE'
    )
  ) %>% 
  group_by(PERIOD, CASE_TYPE) %>% 
  summarize(N_OF_CALLS = n()) %>% 
  ungroup() %>% 
  ggplot(aes(x = PERIOD, y = N_OF_CALLS)) +
    geom_bar(stat = "identity") +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_grid(.~CASE_TYPE) +
    labs(
        x = "Lifecycle",
        y = "# of Calls",
        title = "Number of Calls across Claim File Lifecycle by Process Branch"
      )
```


### 5.1.3. Distribution of Calls between Survey Ready and Close Dates

Most calls are received between survey ready and closing date. Breaking down this period by days passed after survey ready shows that:

* most calls are received 5 to 10 days after survey ready
* most calls come in on the exception flow with peaks until the 20th day

```{r, message=FALSE}
t_calls_ccc <- t_eventlog %>%
  filter(
    CASE_ID %in% t_cutpoints_long$CASE_ID &
      ACTIVITY_TYPE == "KONTAKT CCC" &
      ACTIVITY_CHANNEL == "CALL"
  ) %>%
  select(CASE_ID, MILESTONES, ACTIVITY_EN, EVENT_END)

t_cutpoints %>%
  select(CASE_ID, CASE_TYPE, DECISION_UPPERBOUND, CLOSE_LOWERBOUND) %>%
  filter(!is.na(DECISION_UPPERBOUND)) %>% 
  mutate(
    CASE_TYPE = factor(CASE_TYPE, levels = c("ALTERNATIVE", "STANDARD", "EXCEPTION")),
    THROUGHPUT_TIME = as.numeric(difftime(CLOSE_LOWERBOUND, DECISION_UPPERBOUND, units = "days")),
    THROUGHPUT_TIME_CAT = cut(THROUGHPUT_TIME, c(seq(0, 90, 15), Inf))
  ) %>%
  inner_join(t_calls_ccc, by = "CASE_ID") %>%
  filter(EVENT_END > DECISION_UPPERBOUND & EVENT_END < CLOSE_LOWERBOUND) %>%
  mutate(
    CALL_DIFF = ceiling(as.numeric(difftime(EVENT_END, DECISION_UPPERBOUND, units = "days"))),
    CALL_DIFF_CAT = cut(CALL_DIFF, c(seq(0, 100, 5), Inf))
  ) %>%
  ggplot(aes(CALL_DIFF)) +
  geom_histogram(bins = 50) +
  coord_cartesian(xlim = c(0, 200)) +
  facet_grid(.~CASE_TYPE) +
  labs(
    x = "Days after survey ready",
    y = "# of Calls",
    title = "Number of Calls after Survey Ready by Days Passed"
  )
```

Two main call reasons in this period are:  

* Provide information: peaks at 5-10 days after report
    + Exception flow genereates most provide information calls until approx. 25th day after survey ready
* Reclamation: peaks at 15 days after survey ready

```{r, message=FALSE}
t_cutpoints %>%
  select(CASE_ID, CASE_TYPE, DECISION_UPPERBOUND, CLOSE_LOWERBOUND) %>%
  mutate(
    CASE_TYPE = factor(CASE_TYPE, levels = c("ALTERNATIVE", "STANDARD", "EXCEPTION")),
    THROUGHPUT_TIME = as.numeric(difftime(CLOSE_LOWERBOUND, DECISION_UPPERBOUND, units = "days")),
    THROUGHPUT_TIME_CAT = cut(THROUGHPUT_TIME, c(seq(0, 90, 15), Inf))
  ) %>%
  inner_join(t_calls_ccc, by = "CASE_ID") %>%
  filter(EVENT_END > DECISION_UPPERBOUND & EVENT_END < CLOSE_LOWERBOUND) %>%
  mutate(
    CALL_DIFF = ceiling(as.numeric(difftime(EVENT_END, DECISION_UPPERBOUND, units = "days"))),
    CALL_DIFF_CAT = cut(CALL_DIFF, c(seq(0, 100, 5), Inf)),
    ACTIVITY_EN = factor(case_when(
      ACTIVITY_EN == "Tajekoztatas" ~ "Provide information",
      ACTIVITY_EN == "Reklamacio  OKK-ba tovabbitva" ~ "Reclamation",
      TRUE ~ "Other"
    ), levels = c("Provide information", "Reclamation", "Other"))
  ) %>%
  ggplot(aes(CALL_DIFF)) +
  geom_histogram(bins = 50) +
  coord_cartesian(xlim = c(0, 200)) +
  facet_grid(CASE_TYPE ~ ACTIVITY_EN) +
  labs(
    x = "Days after survey ready",
    y = "# of Calls",
    title = "Number of Calls after Survey Ready by Days Passed"
  )
```


## 5.2. Claims Handling

### 5.2.1. Claims Handling Interactions across Claims Lifecycle

```{r, message=FALSE}
# Genereate bins
by_case_id_okk <- t_events_okk %>%
  select(-MILESTONES) %>% 
  group_by(CASE_ID, CASE_TYPE) %>%
  nest() %>%
  mutate(BINS = map2(data, .$CASE_ID, ~create_bins_3(df = .x, case_id = .y)))


# Graph
by_case_id_okk %>% select(CASE_ID, CASE_TYPE, data, BINS) %>% unnest() %>% 
   mutate(
    PERIOD = case_when(
      is.na(BINS) ~ '1_BEFORE_REPORT',
      BINS == 'REPORT_LOWERBOUND' ~ '2_ON_REPORT',
      BINS == 'REPORT_UPPERBOUND' ~ '3_BETWEEN_REPORT_SURVEYREADY',
      BINS == 'DECISION_LOWERBOUND' ~ '4_ON_SURVEYREADY',
      BINS == 'DECISION_UPPERBOUND' ~ '5_BETWEEN_SURVEYREADY_CLOSE',
      BINS == 'CLOSE_LOWERBOUND' ~ '6_ON_CLOSE',
      BINS == 'CLOSE_UPPERBOUND' ~ '7_AFTER_CLOSE'
    )
  ) %>% 
  group_by(PERIOD) %>% 
  summarize(N_OF_CALLS = n()) %>% 
  ungroup() %>% 
  ggplot(aes(x = PERIOD, y = N_OF_CALLS)) +
    geom_bar(stat = "identity") +
    scale_y_continuous(label = unit_format(unit = "K", scale = 1e-3)) +
    theme(axis.text.x = element_text(angle = 90)) +
    labs(
        x = "Lifecycle",
        y = "# of Claims Handling Interactions",
        title = "Number of Claims Handling Interactions across Claim File Lifecycle"
      )
```


### 5.2.2. Claims Handling Interactions across Claims Lifecycle by Process Branch

```{r, message=FALSE}
# Graph
by_case_id_okk %>% select(CASE_ID, CASE_TYPE, data, BINS) %>% unnest() %>% 
   mutate(
    PERIOD = case_when(
      is.na(BINS) ~ '1_BEFORE_REPORT',
      BINS == 'REPORT_LOWERBOUND' ~ '2_ON_REPORT',
      BINS == 'REPORT_UPPERBOUND' ~ '3_BETWEEN_REPORT_SURVEYREADY',
      BINS == 'DECISION_LOWERBOUND' ~ '4_ON_SURVEYREADY',
      BINS == 'DECISION_UPPERBOUND' ~ '5_BETWEEN_SURVEYREADY_CLOSE',
      BINS == 'CLOSE_LOWERBOUND' ~ '6_ON_CLOSE',
      BINS == 'CLOSE_UPPERBOUND' ~ '7_AFTER_CLOSE'
    )
  ) %>% 
  group_by(PERIOD, CASE_TYPE) %>% 
  summarize(N_OF_CALLS = n()) %>% 
  ungroup() %>% 
  ggplot(aes(x = PERIOD, y = N_OF_CALLS)) +
    geom_bar(stat = "identity") +
    scale_y_continuous(label = unit_format(unit = "K", scale = 1e-3)) +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_grid(.~CASE_TYPE) +
    labs(
        x = "Lifecycle",
        y = "# of Claims Handling Interactions",
        title = "Number of Claims Handling Interactions across Claim File Lifecycle \nby Process Branch"
      )
```

### 5.2.3. Distribution of Claims Handling Interactions between Report and Close Dates

Most interactions happen between survey ready and closing date. Breaking down this period by days passed after survey ready shows that:

* most interactions take place 0 to 5 days after survey ready

```{r, message=FALSE}
t_events_okk <- t_eventlog %>%
  filter(
    CASE_ID %in% t_cutpoints_long$CASE_ID &
      ACTIVITY_TYPE == "KONTAKT OKK"
  ) %>%
  select(CASE_ID, MILESTONES, EVENT_END, USER_ID) %>%
  mutate(DEPT = stringr::str_extract(USER_ID, "[^OKK/].*?(?=\\\\)")) %>%
  mutate(DEPT = case_when(
    DEPT == "Gepjarmu/szakertok" ~ "Car/Experts",
    DEPT == "Logisztikai csoport/Levelfeldolgozo" ~ "Logistics/Mailroom",
    TRUE ~ "Other"
  ))

t_cutpoints %>%
  select(CASE_ID, CASE_TYPE,DECISION_UPPERBOUND, CLOSE_LOWERBOUND) %>%
  mutate(
    CASE_TYPE = factor(CASE_TYPE, levels = c("ALTERNATIVE", "STANDARD", "EXCEPTION")),
    THROUGHPUT_TIME = as.numeric(difftime(CLOSE_LOWERBOUND, DECISION_UPPERBOUND, units = "days")),
    THROUGHPUT_TIME_CAT = cut(THROUGHPUT_TIME, c(seq(0, 90, 15), Inf))
  ) %>%
  inner_join(t_events_okk, by = "CASE_ID") %>%
  filter(EVENT_END > DECISION_UPPERBOUND & EVENT_END < CLOSE_LOWERBOUND) %>%
  mutate(
    CALL_DIFF = ceiling(as.numeric(difftime(EVENT_END, DECISION_UPPERBOUND, units = "days"))),
    CALL_DIFF_CAT = cut(CALL_DIFF, c(seq(0, 100, 5), Inf))
  ) %>%
  ggplot(aes(CALL_DIFF)) +
  geom_histogram(bins = 50) +
  coord_cartesian(xlim = c(0, 200)) +
  facet_grid(. ~ CASE_TYPE) +
  labs(
    x = "Days after survey ready",
    y = "# of Calls",
    title = "Number of Interactions after Survey Ready by Days Passed"
  )
```

There is no difference in peak point between process branches.

```{r, message=FALSE}
t_cutpoints %>%
  select(CASE_ID, CASE_TYPE, DECISION_UPPERBOUND, CLOSE_LOWERBOUND) %>%
  mutate(
    CASE_TYPE = factor(CASE_TYPE, levels = c("ALTERNATIVE", "STANDARD", "EXCEPTION")),
    THROUGHPUT_TIME = as.numeric(difftime(CLOSE_LOWERBOUND, DECISION_UPPERBOUND, units = "days")),
    THROUGHPUT_TIME_CAT = cut(THROUGHPUT_TIME, c(seq(0, 90, 15), Inf))
  ) %>%
  inner_join(t_events_okk, by = "CASE_ID") %>%
  filter(EVENT_END > DECISION_UPPERBOUND & EVENT_END < CLOSE_LOWERBOUND) %>%
  mutate(
    CALL_DIFF = ceiling(as.numeric(difftime(EVENT_END, DECISION_UPPERBOUND, units = "days"))),
    CALL_DIFF_CAT = cut(CALL_DIFF, c(seq(0, 100, 5), Inf))
  ) %>%
  ggplot(aes(CALL_DIFF)) +
  geom_histogram(bins = 50) +
  coord_cartesian(xlim = c(0, 200)) +
  facet_grid(DEPT ~ CASE_TYPE) +
  labs(
    x = "Days after survey ready",
    y = "# of Calls",
    title = "Number of Interactions after Survey Ready by Days Passed"
  )
```