---
title: "CCC Activities across the Casco and Home Claim Management Lifecycle (A Business Case Outline)"
author: "János Poór"
date: 'April 26, 2019'
output: rmdformats::readthedown
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r, message = FALSE, echo = TRUE, include = FALSE}
library(config)
library(dplyr)
library(ggplot2)
library(purrr)
library(lubridate)
library(gridExtra)
library(tidyr)
library(scales)
library(stringr)
library(forcats)
```


```{r, include=FALSE}
# Data Extraction #######################################################################

# Set JAVA_HOME, set max. memory, and load rJava library
Sys.setenv(JAVA_HOME = "C:\\Program Files\\Java\\jre1.8.0_171")
options(java.parameters = "-Xmx2g")
library(rJava)

# Output Java version
.jinit()
print(.jcall("java/lang/System", "S", "getProperty", "java.version"))

# Load RJDBC library
library(RJDBC)

# Get credentials
datamnr <-
  config::get("datamnr", file = "C:\\Users\\PoorJ\\Projects\\config.yml")

# Create connection driver
jdbcDriver <-
  JDBC(driverClass = "oracle.jdbc.OracleDriver", classPath = "C:\\Users\\PoorJ\\Desktop\\ojdbc7.jar")

# Open connection: kontakt
jdbcConnection <-
  dbConnect(
    jdbcDriver,
    url = datamnr$server,
    user = datamnr$uid,
    password = datamnr$pwd
  )

# Fetch Home data
query_branches <- "SELECT * FROM T_CLAIMS_HOME_DISTINCT"
t_home_branches <- dbGetQuery(jdbcConnection, query_branches)

query_branches_paid <- "SELECT * FROM T_CLAIMS_HOME_DISTINCT_PAID"
t_home_branches_paid <- dbGetQuery(jdbcConnection, query_branches_paid)

query_cutpoints <- "SELECT * FROM T_CLAIMS_HOME_MILESTONES"
t_home_cutpoints <- dbGetQuery(jdbcConnection, query_cutpoints)

query_eventlog <-
"SELECT * FROM T_CLAIMS_HOME_KONTAKT_EVENTLOG"
t_home_eventlog <- dbGetQuery(jdbcConnection, query_eventlog)



# Fetch Casco data
query_branches <- "SELECT * FROM T_CLAIMS_MILESTONES"
t_casco_branches <- dbGetQuery(jdbcConnection, query_branches)

query_cutpoints <- "SELECT * FROM T_CLAIMS_MILESTONES_CLEANED"
t_casco_cutpoints <- dbGetQuery(jdbcConnection, query_cutpoints)

query_eventlog <-
"SELECT * FROM T_CLAIMS_PA_OUTPUT_CCC_OKK a WHERE milestones IS NOT NULL
AND EXISTS (SELECT 1 FROM T_CLAIMS_MILESTONES_CLEANED b WHERE a.case_id = b.case_id)"
t_casco_eventlog <- dbGetQuery(jdbcConnection, query_eventlog)


# Close db connection: kontakt
dbDisconnect(jdbcConnection)


# Transform data
t_home_eventlog <- t_home_eventlog %>% mutate_at(vars(EVENT_END), ymd_hms)
t_home_branches <- t_home_branches %>% mutate_at(vars(F_KARIDO, F_KARBEIDO, F_UTALAS_FIRST), ymd_hms)
t_home_branches_paid <- t_home_branches_paid %>% mutate_at(vars(F_KARIDO, F_KARBEIDO, F_UTALAS_FIRST), ymd_hms)
t_casco_eventlog <- t_casco_eventlog %>% mutate_at(vars(EVENT_END), ymd_hms)
t_casco_branches <- t_casco_branches %>% mutate_at(vars(CLAIM_REPORT_DATE, CLAIM_DECISION_DATE, CLAIM_CLOSE_DATE), ymd_hms)
```


# Outline of a Business Case

Most customer interactions during claim management are done through calls. There is a **clear distinction in the pattern of calls** across the claim management lifecycle for casco and home products. Business question: which pattern fits better the customer relations strategy of the company and what improvements can be done?

The Background:

* Managment of claim files trigger customer interactions for the Contact Center. These interactions are initiated and responded via different channels (call, online, email, etc).  
* Process Analytics genereated for all managed home and casco claims in 2017-2018     
	+ a database of interactions
	+ a database of claim management lifecycles
* Process Analytics delivers:   
	+ an overview of the distribution of interactions across different channels
	+ a **breakdown of the concentration of interactions** across claim management lifecycles  


***


# Contact Center Interactions 

The majority of interactions during claim management happens through calls. PWEB interacions of home products is considerable.

```{r, message=FALSE}
int_casco <- t_casco_eventlog %>% 
  filter(ACTIVITY_TYPE == "KONTAKT CCC") %>% 
  group_by(ACTIVITY_CHANNEL) %>% 
  summarize(TOTAL_INTERACTIONS = length(CASE_ID),
            DISTINCT_REQUESTS = length(unique(CASE_ID)),
            INTERACTION_PER_REQUEST = length(CASE_ID)/length(unique(CASE_ID))) %>% 
  ungroup() %>% 
  mutate(PRODUCT_LINE = "CASCO")

  
int_home <- t_home_eventlog %>% 
  filter(ACTIVITY_TYPE == "KONTAKT CCC") %>% 
  group_by(ACTIVITY_CHANNEL) %>% 
  summarize(TOTAL_INTERACTIONS = length(CASE_ID),
            DISTINCT_REQUESTS = length(unique(CASE_ID)),
            INTERACTION_PER_REQUEST = length(CASE_ID)/length(unique(CASE_ID))) %>% 
  ungroup() %>% 
  mutate(PRODUCT_LINE = "HOME")
  
bind_rows(int_casco, int_home) %>% 
              tidyr::gather(-ACTIVITY_CHANNEL, -PRODUCT_LINE, key = METRIC, value = VALUE) %>%
  mutate(METRIC = factor(METRIC,levels = c("TOTAL_INTERACTIONS", "DISTINCT_REQUESTS", "INTERACTION_PER_REQUEST"))) %>% 
  ggplot(aes(x = ACTIVITY_CHANNEL, y = VALUE)) +
    geom_bar(stat = "identity") +
    theme(strip.text.y = element_text(angle = 0)) +
    facet_grid(METRIC~PRODUCT_LINE, scales = "free") +
    labs(
        x = "Interaction channel",
        y = "Counts",
        title = "Contact Center Interaction Types \nacross Casco and Home Claim Files (2017-2018)"
      )

```

```{r, message=FALSE, eval = FALSE}
# Casco lifecycles ######################################################################
# Define lifecycle cutpoints
t_casco_cutpoints_long <- t_casco_cutpoints %>%
  filter(REPORT_LOWERBOUND < as.Date("2018-07-01")) %>%
  mutate_at(vars(REPORT_LOWERBOUND:CLOSE_UPPERBOUND), ymd_hms) %>%
  select(-DECISION_LOWERBOUND, -DECISION_UPPERBOUND) %>% 
  tidyr::gather(-CASE_ID, -CASE_TYPE, -MILESTONES, key = CUTPOINT, value = CUTDATE) %>%
  arrange(CASE_ID, CUTPOINT) %>% 
  filter(!is.na(CUTDATE))


# Org specific event seqs
t_casco_events_ccc <- t_casco_eventlog %>%
  filter(
        CASE_ID %in% t_casco_cutpoints_long$CASE_ID
        & ACTIVITY_TYPE == "KONTAKT CCC"
        #& ACTIVITY_CHANNEL == "CALL"
        ) %>%
  select(CASE_ID, CASE_TYPE, MILESTONES, EVENT_END, ACTIVITY_CHANNEL)


t_casco_events_okk <- t_casco_eventlog %>%
  filter(
        CASE_ID %in% t_casco_cutpoints_long$CASE_ID &
        ACTIVITY_TYPE == "KONTAKT OKK") %>%
  select(CASE_ID, CASE_TYPE, MILESTONES, EVENT_END)


# Define Func to Compute Bins
create_bins_casco_2 <- function(df, case_id) {
  t_cutpoints_long_filtered <- t_casco_cutpoints_long[t_casco_cutpoints_long$CASE_ID == case_id, ] %>% arrange(CUTDATE)
  as.character(cut(df$EVENT_END,
    breaks = c(t_cutpoints_long_filtered$CUTDATE, Inf),
    labels = t_cutpoints_long_filtered$CUTPOINT
  ))
}


# Genereate bins
by_case_id_casco_ccc <- t_casco_events_ccc %>%
  select(-MILESTONES) %>% 
  group_by(CASE_ID, CASE_TYPE, ACTIVITY_CHANNEL) %>%
  nest() %>%
  mutate(BINS = map2(data, .$CASE_ID, ~create_bins_casco_2(df = .x, case_id = .y)))
```


```{r, message=FALSE, eval=FALSE}
# Home lifecycles ######################################################################
# Define lifecycle cutpoints
t_home_cutpoints_long <- t_home_cutpoints %>%
  #filter(REPORT_LOWERBOUND < as.Date("2018-07-01")) %>%
  filter(REPORT_LOWERBOUND != CLOSE_LOWERBOUND) %>% 
  mutate_at(vars(REPORT_LOWERBOUND:CLOSE_UPPERBOUND), ymd_hms) %>%
  #select(-DECISION_LOWERBOUND, -DECISION_UPPERBOUND) %>% 
  tidyr::gather(-CASE_ID, -CASE_TYPE, -PRODUCT_CODE, key = CUTPOINT, value = CUTDATE) %>%
  arrange(CASE_ID, CUTPOINT) %>% 
  filter(!is.na(CUTDATE))


# Org specific event seqs
t_home_events_ccc <- t_home_eventlog %>%
  filter(
        CASE_ID %in% t_home_cutpoints_long$CASE_ID
        & ACTIVITY_TYPE == "KONTAKT CCC"
        #& ACTIVITY_CHANNEL == "CALL"
        ) %>%
  select(CASE_ID, CASE_TYPE, EVENT_END, ACTIVITY_CHANNEL)


t_home_events_okk <- t_home_eventlog %>%
  filter(
        CASE_ID %in% t_home_cutpoints_long$CASE_ID &
        ACTIVITY_TYPE == "KONTAKT OKK") %>%
  select(CASE_ID, CASE_TYPE, EVENT_END)


# Define Func to Compute Bins
create_bins_home_2 <- function(df, case_id) {
  t_cutpoints_long_filtered <- t_home_cutpoints_long[t_home_cutpoints_long$CASE_ID == case_id, ] %>% arrange(CUTDATE)
  as.character(cut(df$EVENT_END,
    breaks = c(t_cutpoints_long_filtered$CUTDATE, Inf),
    labels = t_cutpoints_long_filtered$CUTPOINT
  ))
}


# Genereate bins
by_case_id_home_ccc <- t_home_events_ccc %>%
  #select(-MILESTONES) %>% 
  group_by(CASE_ID, CASE_TYPE, ACTIVITY_CHANNEL) %>%
  nest() %>%
  mutate(BINS = map2(data, .$CASE_ID, ~create_bins_home_2(df = .x, case_id = .y)))
```

```{r, message=FALSE, eval=FALSE}
# Merge
casco <- by_case_id_casco_ccc %>%
  select(CASE_ID, CASE_TYPE, ACTIVITY_CHANNEL, data, BINS) %>%
  unnest() %>%
  mutate(
    PERIOD = factor(case_when(
                      is.na(BINS) ~ "BEFORE REPORT",
                      BINS == "REPORT_LOWERBOUND" ~ "ON REPORT",
                      BINS == "REPORT_UPPERBOUND" ~ "BETWEEN REPORT & CLOSE",
                      BINS == "CLOSE_LOWERBOUND" ~ "ON CLOSE",
                      BINS == "CLOSE_UPPERBOUND" ~ "AFTER CLOSE"
                            ),
              levels = c("BEFORE REPORT", "ON REPORT", "BETWEEN REPORT & CLOSE", "ON CLOSE", "AFTER CLOSE")),
    PRODUCT_LINE = "CASCO",
    CASE_TYPE = case_when(
      CASE_TYPE == "ALTERNATIVE" ~ "ALTER/SIMPLE",
      TRUE ~ CASE_TYPE
    )
  )

home <- by_case_id_home_ccc %>% select(CASE_ID, CASE_TYPE, ACTIVITY_CHANNEL, data, BINS) %>% unnest() %>% 
  mutate(
    PERIOD = factor(case_when(
                      is.na(BINS) ~ "BEFORE REPORT",
                      BINS == "REPORT_LOWERBOUND" ~ "ON REPORT",
                      BINS == "REPORT_UPPERBOUND" ~ "BETWEEN REPORT & CLOSE",
                      BINS == "CLOSE_LOWERBOUND" ~ "ON CLOSE",
                      BINS == "CLOSE_UPPERBOUND" ~ "AFTER CLOSE"
                            ),
              levels = c("BEFORE REPORT", "ON REPORT", "BETWEEN REPORT & CLOSE", "ON CLOSE", "AFTER CLOSE")),
    PRODUCT_LINE = 'HOME',
    CASE_TYPE = case_when(
      CASE_TYPE == 'Simple' ~ 'ALTER/SIMPLE',
      CASE_TYPE == 'Standard' ~ 'STANDARD',
      CASE_TYPE == 'Exception' ~ 'EXCEPTION'
    )
  )

t_lifecycles <- bind_rows(casco, home)

# Write to local storage
write.csv(t_lifecycles,
          here::here("Data", "t_lifecycles_home_casco.csv"),
          row.names = FALSE)
```

***


# Comparison of Contact Center Interactions across the Claim Management Lifecycle

For all interaction channels concentration of acitivities are broken down across the milestones of claim management.
The two major lifecycle milestones are:  

* Date of reporting the claim  
* Date of closing the claim  

The two cutpoints yield five lifecylcle sequences:  

* Before reporting  
* The day of rerporting  
* Between reporting and closing  
* The day of closing  
* After closing  


The clearest difference in patterns is that:  

* most calls for casco products are done between report and closing 
* while for home products most calls are done on the day of reporting  


> This suggests that for home products calls are mostly reporting calls while for casco produts they are interactions generated by the process of claim file management itself.

```{r, message=FALSE}
# Load from local cache
t_lifecycles <- read.csv(here::here("Data", "t_lifecycles_home_casco.csv"), stringsAsFactors = FALSE) %>% 
  mutate(PERIOD = factor(PERIOD, levels = c("BEFORE REPORT", "ON REPORT", "BETWEEN REPORT & CLOSE", "ON CLOSE", "AFTER CLOSE")))
```

```{r, message=FALSE}
# Graph
t_lifecycles %>% 
group_by(PRODUCT_LINE, PERIOD, ACTIVITY_CHANNEL) %>%
  summarize(N_OF_CALLS = n()) %>%
  ungroup() %>%
  group_by(PRODUCT_LINE) %>% 
  mutate(RATIO = N_OF_CALLS/sum(N_OF_CALLS)) %>% 
  ungroup() %>% 
  ggplot(aes(x = PERIOD, y = RATIO)) +
    geom_bar(stat = "identity") +
    scale_y_continuous(labels = percent) +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_grid(PRODUCT_LINE~ACTIVITY_CHANNEL) + 
    labs(
        x = "Phase of Claim Management Lifecycle",
        y = "# of Interactions",
        title = "Distriubution of Contact Center Interactions \nacross the Claim Management Lifecycle"
      )
```

***


# Comparison of Contact Center Interactions across the Claim Management Lifecycle by Process Branch

## Casco

The close-up on process branches of casco shows that most calls are generated by the exception flow between report and closing that  suggests that these calls are done for claims that are off the happyflow of claim management. 

```{r, message=FALSE}
# Graph
t_lifecycles %>% 
filter(PRODUCT_LINE == "CASCO") %>% 
mutate(CASE_TYPE = factor(CASE_TYPE, levels = c('ALTER/SIMPLE', 'STANDARD', 'EXCEPTION'))) %>% 
group_by(PERIOD, CASE_TYPE, ACTIVITY_CHANNEL) %>%
  summarize(N_OF_CALLS = n()) %>%
  ungroup() %>%
  group_by(CASE_TYPE) %>% 
  mutate(RATIO = N_OF_CALLS/sum(N_OF_CALLS)) %>% 
  ungroup() %>% 
  ggplot(aes(x = PERIOD, y = RATIO)) +
    geom_bar(stat = "identity") +
    scale_y_continuous(labels = percent) +
    theme(axis.text.x = element_text(angle = 90),
          strip.text.y = element_text(angle = 0)) +
    facet_grid(CASE_TYPE~ACTIVITY_CHANNEL) + 
    labs(
        x = "Lifecycle",
        y = "# of Calls",
        title = "Casco Interactions by Process Branch across Claim File Lifecycle"
      )
```

## Home

For home products most calls are done on report day for both the standard and the exception flow of the process that suggests that these calls are initial claim reports by customers.

```{r, message=FALSE}
# Graph
t_lifecycles %>% 
filter(PRODUCT_LINE == "HOME") %>% 
mutate(CASE_TYPE = factor(CASE_TYPE, levels = c('ALTER/SIMPLE', 'STANDARD', 'EXCEPTION'))) %>% 
group_by(PERIOD, CASE_TYPE, ACTIVITY_CHANNEL) %>%
  summarize(N_OF_CALLS = n()) %>%
  ungroup() %>%
  group_by(CASE_TYPE) %>% 
  mutate(RATIO = N_OF_CALLS/sum(N_OF_CALLS)) %>% 
  ungroup() %>% 
  ggplot(aes(x = PERIOD, y = RATIO)) +
    geom_bar(stat = "identity") +
    scale_y_continuous(labels = percent) +
    theme(axis.text.x = element_text(angle = 90),
          strip.text.y = element_text(angle = 0)) +
    facet_grid(CASE_TYPE~ACTIVITY_CHANNEL) + 
    labs(
        x = "Lifecycle",
        y = "# of Calls",
        title = "Home Interactions by Process Branch across Claim File Lifecycle"
      )
```