---
title: "Home Claims: Branches and Interactions"
author: "János Poór"
date: 'April 24, 2019'
output: rmdformats::readthedown
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r, message = FALSE, echo = TRUE, include = FALSE}
library(config)
library(dplyr)
library(ggplot2)
library(purrr)
library(lubridate)
library(gridExtra)
library(tidyr)
library(scales)
library(stringr)
```


```{r, include=FALSE}
# Data Extraction #######################################################################

# Set JAVA_HOME, set max. memory, and load rJava library
Sys.setenv(JAVA_HOME = "C:\\Program Files\\Java\\jre1.8.0_171")
options(java.parameters = "-Xmx2g")
library(rJava)

# Output Java version
.jinit()
print(.jcall("java/lang/System", "S", "getProperty", "java.version"))

# Load RJDBC library
library(RJDBC)

# Get credentials
datamnr <-
  config::get("datamnr", file = "C:\\Users\\PoorJ\\Projects\\config.yml")

# Create connection driver
jdbcDriver <-
  JDBC(driverClass = "oracle.jdbc.OracleDriver", classPath = "C:\\Users\\PoorJ\\Desktop\\ojdbc7.jar")

# Open connection: kontakt
jdbcConnection <-
  dbConnect(
    jdbcDriver,
    url = datamnr$server,
    user = datamnr$uid,
    password = datamnr$pwd
  )

# Fetch data
query_branches <- "SELECT * FROM T_CLAIMS_HOME_DISTINCT"
t_branches <- dbGetQuery(jdbcConnection, query_branches)

query_branches_paid <- "SELECT * FROM T_CLAIMS_HOME_DISTINCT_PAID"
t_branches_paid <- dbGetQuery(jdbcConnection, query_branches_paid)

query_cutpoints <- "SELECT * FROM T_CLAIMS_HOME_MILESTONES"
t_cutpoints <- dbGetQuery(jdbcConnection, query_cutpoints)

query_eventlog <-
"SELECT * FROM T_CLAIMS_HOME_KONTAKT_EVENTLOG"
t_eventlog <- dbGetQuery(jdbcConnection, query_eventlog)


# Close db connection: kontakt
dbDisconnect(jdbcConnection)


# Transform data
t_eventlog <- t_eventlog %>% mutate_at(vars(EVENT_END), ymd_hms)

t_branches <- t_branches %>% mutate_at(vars(F_KARIDO, F_KARBEIDO, F_UTALAS_FIRST), ymd_hms)

t_branches_paid <- t_branches_paid %>% mutate_at(vars(F_KARIDO, F_KARBEIDO, F_UTALAS_FIRST), ymd_hms)
```

# 1. TL;DR

Home claims are defined by excluding life related dangers (accident, pet) and special riders like assistance. In 2017-2018 there were
275K paid claim of this sort. In Kontakt system we have found interacitons for 220K of those claims. 117K had Contact Center (not including external CC) interactions and 86K had Claim Handling Center interactions.

Outline of the main conclusions of the analysis of Home claims process branches and interactions:  

* Process branches  
	+ Simple claim management for about 20% of cases
	+ Proporiton of standard flow (happyflow) is about 64%
	+ Exception flow is 15%
* Interactions (Kontakt system entries) 
	+ Those cases that have Contact Center interactions have on average 1.8
	+ Those cases that have Claims Handling interactions have on average 1.5
* Lifecycles  
	+ Most Contact Center calls happen on date of report in stadard flow
	+ Most Claims Handling interactions happen after closing of claim
	
***	

# 2. Overview of Home Claims

## 2.1. Monthly Volume and Throughput Time of Reported Casco Claims

Dataset contains 275K reported and closed Home claims that were paid out between 2017/01 and 2018/12. Monthly fluctuation reflects seasonal peaks in summer months.

```{r, message=FALSE}
p1 <- t_branches %>%
  #filter(CLAIM_REPORT_DATE < as.Date("2018-07-01")) %>%
  mutate(CLAIM_REPORT_MONTH = lubridate::floor_date(F_KARBEIDO, unit = "month")) %>%
  group_by(CLAIM_REPORT_MONTH) %>%
  summarize(COUNT_REPORTED_CLAIMS = n()) %>%
  ungroup() %>%
  ggplot(aes(x = CLAIM_REPORT_MONTH, y = COUNT_REPORTED_CLAIMS)) +
  geom_line() +
  labs(
    x = "Month",
    y = "# of Reported Home Claims",
    title = "Number of Reported Home Claims per Month"
  )

p2 <- t_branches %>%
  #filter(CLAIM_REPORT_DATE < as.Date("2018-07-01")) %>%
  mutate(
    CLAIM_REPORT_MONTH = lubridate::floor_date(F_KARBEIDO, unit = "month"),
    THROUGHPUT_TIME = difftime(F_UTALAS_FIRST, F_KARBEIDO, units = "days")
  ) %>%
  group_by(CLAIM_REPORT_MONTH) %>%
  summarize(AVG_THROUGHPUT = mean(THROUGHPUT_TIME)) %>%
  ungroup() %>%
  ggplot(aes(x = CLAIM_REPORT_MONTH, y = AVG_THROUGHPUT)) +
  geom_line() +
  labs(
    x = "Month",
    y = "Throughput Time (days)",
    title = "Throughput Time Reported Home Claims per Month"
  )

grid.arrange(p1, p2, nrow = 2)
```


## 2.2. Monthly Volume and Throughput Time By Process Branch

Process has three main branches:  

* Simple: claim management for simple claims (typically broken glass)
* Standard: claim management with survey without pending states (happyflow)   
* Exception: claim management with survey with pending states

```{r, message=FALSE}
p3 <- t_branches %>%
  #filter(CLAIM_REPORT_DATE < as.Date("2018-07-01")) %>%
  mutate(CLAIM_REPORT_MONTH = lubridate::floor_date(F_KARBEIDO, unit = "month")) %>%
  group_by(CLAIM_REPORT_MONTH, CASE_TYPE) %>%
  summarize(COUNT_REPORTED_CLAIMS = n()) %>%
  ungroup() %>%
  mutate(CASE_TYPE = factor(CASE_TYPE, levels=c('Simple', 'Standard','Exception'))) %>% 
  ggplot(aes(x = CLAIM_REPORT_MONTH, y = COUNT_REPORTED_CLAIMS)) +
  geom_line() +
  theme(axis.text.x = element_text(angle = 90)) +
  facet_wrap(~ CASE_TYPE) +
  labs(
    x = "Month",
    y = "# of Reported Home Claims",
    title = "Number of Reported Home Claims per Month"
  )

p4 <- t_branches %>%
  #filter(CLAIM_REPORT_DATE < as.Date("2018-07-01")) %>%
  mutate(
    CLAIM_REPORT_MONTH = lubridate::floor_date(F_KARBEIDO, unit = "month"),
    THROUGHPUT_TIME = difftime(F_UTALAS_FIRST, F_KARBEIDO, units = "days")
  ) %>%
  group_by(CLAIM_REPORT_MONTH, CASE_TYPE) %>%
  summarize(AVG_THROUGHPUT = mean(THROUGHPUT_TIME)) %>%
  ungroup() %>%
  mutate(CASE_TYPE = factor(CASE_TYPE, levels=c('Simple', 'Standard','Exception'))) %>% 
  ggplot(aes(x = CLAIM_REPORT_MONTH, y = AVG_THROUGHPUT)) +
  geom_line() +
  theme(axis.text.x = element_text(angle = 90)) +
  facet_wrap(~ CASE_TYPE) +
  labs(
    x = "Month",
    y = "Throughput Time (days)",
    title = "Throughput Time Reported Home Claims per Month"
  )

grid.arrange(p3, p4, nrow = 2)
```

***



<!-- # 3. Analysis of Interactions -->

<!-- ## 3.1. Average Interactions per Claim File -->

<!-- For both  Contact Center and Claims Handling we can compute how many times operators interacted with the claim file in the workflow system (Kontakt). -->

<!-- Not every claim file has Contact Center interactions. The average number of Contact Center interactions needs to be differentiated:   -->

<!-- * Contact Center General: average across ALL claim files   -->
<!-- * Contact Center Special: average accross ONLY THOSE claim files that had Contact Center interactions -->

```{r, message=FALSE, eval=FALSE}
# Compute interactions per case
t_interaction_counts <- t_eventlog %>%
  group_by(CASE_ID, ACTIVITY_TYPE) %>%
  summarize(COUNT_OF_ACTIVITY = n()) %>%
  ungroup() %>%
  tidyr::spread(key = ACTIVITY_TYPE, value = COUNT_OF_ACTIVITY, fill = 0)

names(t_interaction_counts) <- c("CASE_ID", "KONTAKT_CCC", "KONTAKT_OKK")

# Add interactions to base table

# Define claim files that have CCC interactions
t_ccc_special <- t_branches_paid %>%
  #filter(CLAIM_REPORT_DATE < as.Date("2018-07-01")) %>%
  mutate(CLAIM_REPORT_MONTH = lubridate::floor_date(F_KARBEIDO, unit = "month"),
         CASE_ID = F_PAID) %>%
  left_join(t_interaction_counts, by = c("CASE_ID")) %>%
  filter(KONTAKT_CCC != 0) %>% 
  group_by(CLAIM_REPORT_MONTH) %>%
  summarize(
    ContactCenterSpecial = mean(KONTAKT_CCC, na.rm = TRUE))

# Define interactions across all claim files
t_branches_paid %>%
  #filter(CLAIM_REPORT_DATE < as.Date("2018-07-01")) %>%
  mutate(CLAIM_REPORT_MONTH = lubridate::floor_date(F_KARBEIDO, unit = "month"),
         CASE_ID = F_PAID) %>%
  left_join(t_interaction_counts, by = c("CASE_ID")) %>%
  group_by(CLAIM_REPORT_MONTH) %>%
  summarize(
    ContactCenterGeneral = mean(KONTAKT_CCC, na.rm = TRUE),
    ClaimsHandling = mean(KONTAKT_OKK, na.rm = TRUE)
  ) %>%
  ungroup() %>%
  left_join(t_ccc_special, by = c("CLAIM_REPORT_MONTH")) %>%
  tidyr::gather(-CLAIM_REPORT_MONTH, key = ORG, value = AVG_INT) %>% 
  ggplot(aes(x = CLAIM_REPORT_MONTH, y = AVG_INT)) +
    geom_line() +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_grid(.~ORG) +
    labs(
      x = "Month",
      y = "# of Interactions per Claim File",
      title = "Number of Average Interactions per Claim File"
    )
```


<!-- ## 3.2. Average Interactions per Claim File By Process Branch -->


```{r, message=FALSE, eval=FALSE}
# Define claim files that have CCC interactions
t_ccc_special_by_case_type <- t_branches_paid %>%
  #filter(CLAIM_REPORT_DATE < as.Date("2018-07-01")) %>%
  mutate(CLAIM_REPORT_MONTH = lubridate::floor_date(F_KARBEIDO, unit = "month"),
         CASE_ID = F_PAID) %>%
  left_join(t_interaction_counts, by = c("CASE_ID")) %>%
  filter(KONTAKT_CCC != 0) %>%
  mutate(CASE_TYPE = factor(CASE_TYPE, levels=c('Simple', 'Standard','Exception'))) %>% 
  group_by(CLAIM_REPORT_MONTH, CASE_TYPE) %>%
  summarize(
    ContactCenterSpecial = mean(KONTAKT_CCC, na.rm = TRUE))


# Add interactions to base table
t_branches_paid %>%
  #filter(CLAIM_REPORT_DATE < as.Date("2018-07-01")) %>%
  mutate(CLAIM_REPORT_MONTH = lubridate::floor_date(F_KARBEIDO, unit = "month"),
         CASE_ID = F_PAID) %>%
  left_join(t_interaction_counts, by = c("CASE_ID")) %>%
  mutate(CASE_TYPE = factor(CASE_TYPE, levels=c('Simple', 'Standard','Exception'))) %>% 
  group_by(CLAIM_REPORT_MONTH, CASE_TYPE) %>%
  summarize(
    ContactCenter = mean(KONTAKT_CCC, na.rm = TRUE),
    ClaimsHandling = mean(KONTAKT_OKK, na.rm = TRUE)
  ) %>%
  ungroup() %>%
  left_join(t_ccc_special_by_case_type, by = c("CLAIM_REPORT_MONTH", "CASE_TYPE")) %>%
  tidyr::gather(-CLAIM_REPORT_MONTH, -CASE_TYPE, key = ORG, value = AVG_INT) %>% 
  ggplot(aes(x = CLAIM_REPORT_MONTH, -CASE_TYPE, y = AVG_INT)) +
    geom_line() +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_grid(CASE_TYPE~ORG) +
    labs(
      x = "Month",
      y = "# of Interactions per Claim File",
      title = "Number of Average Interactions per Claim File"
    )
```


<!-- ## 3.3. Breakdown of Claims Handling Interactions by Department -->

```{r, message=FALSE, eval=FALSE}
# Compute interactions per case
t_interaction_counts_claimsdept <- t_eventlog %>%
  filter(ACTIVITY_TYPE == "KONTAKT OKK") %>%
  mutate(DEPT = stringr::str_extract(USER_ID, "[^OKK/].*?(?=\\\\)")) %>%
  mutate(DEPT = case_when(
    DEPT == "Vagyon/Vezeto szakerto" ~ "Home/Experts",
    DEPT == "Logisztikai csoport/Irattaros" ~ "Logistics",
    DEPT == "Logisztikai csoport/Levelfeldolgozo" ~ "Logistics",
    DEPT == "Penzugy" ~ "Financial",
    TRUE ~ "Other"
  )) %>%
  group_by(CASE_ID, DEPT) %>%
  summarize(COUNT_OF_ACTIVITY = n()) %>%
  ungroup()

# Add interactions to base table
t_branches_paid %>%
  #filter(CLAIM_REPORT_DATE < as.Date("2018-07-01")) %>%
  mutate(CLAIM_REPORT_MONTH = lubridate::floor_date(F_KARBEIDO, unit = "month"),
         CASE_ID = F_PAID) %>%
  select(CASE_ID, CLAIM_REPORT_MONTH) %>%
  left_join(t_interaction_counts_claimsdept, by = c("CASE_ID")) %>%
  filter(!is.na(DEPT) & DEPT != "Other") %>%
  group_by(CLAIM_REPORT_MONTH, DEPT) %>%
  summarize(AVG_INT = mean(COUNT_OF_ACTIVITY, na.rm = TRUE)) %>%
  ungroup() %>%
  ggplot(aes(x = CLAIM_REPORT_MONTH, y = AVG_INT, group = DEPT, color = DEPT)) +
  geom_line() +
  theme(axis.text.x = element_text(angle = 90)) +
  geom_point() +
  labs(
    x = "Month",
    y = "# of Interactions per Claim File",
    title = "Number of Average Interactions per Claim File\nby Claims Handling Department"
  )
```


<!-- ## 3.4. Breakdown of Claims Handling Interactions by Department by Process Branch -->

```{r, message=FALSE, eval=FALSE}
# Add interactions to base table
t_branches_paid %>%
  #filter(CLAIM_REPORT_DATE < as.Date("2018-07-01")) %>%
  mutate(CLAIM_REPORT_MONTH = lubridate::floor_date(F_KARBEIDO, unit = "month"),
         CASE_ID = F_PAID) %>%
  select(CASE_ID, CLAIM_REPORT_MONTH, CASE_TYPE) %>% 
  left_join(t_interaction_counts_claimsdept, by = c("CASE_ID")) %>% 
  filter(!is.na(DEPT) & DEPT != "Other") %>% 
  group_by(CLAIM_REPORT_MONTH, DEPT, CASE_TYPE) %>% 
  summarize(AVG_INT = mean(COUNT_OF_ACTIVITY, na.rm = TRUE)) %>% 
  ungroup() %>%
  mutate(CASE_TYPE = factor(CASE_TYPE, levels=c('Simple', 'Standard','Exception'))) %>% 
  ggplot(aes(x = CLAIM_REPORT_MONTH, y = AVG_INT, group = DEPT, color = DEPT)) +
  geom_line() +
  geom_point() +
  theme(axis.text.x = element_text(angle = 90)) +
  facet_grid(.~CASE_TYPE) +
  labs(
    x = "Month",
    y = "# of Interactions per Claim File",
    title = "Number of Average Interactions per Claim File\nby Claims Handling Department"
  )
```

<!-- *** -->



# 3. Analysis of Claims Lifecycle (2 Cutpoints)

Claim file lifecycle can be computed from ABLAK status data. The two major lifecycle cutpoints are:  

* Date of reporting the claim  
* Date of closing the claim file (defined as the date of first payment for Home)

The two cutpoints yield five lifecylcle sequences:  

* Before reporting  
* The day of rerporting  
* Between reporting and closing  
* The day of closing  
* After closing  


## 3.1. Contact Center

### 3.1.1. Contact Center Calls across Claims Lifecycle

Breakdown of calls for those claim files that had calls (note: not every claim file has Contact Center interactions, see previous section). The pattern shows that most calls are realted to claim reporting.

```{r, message=FALSE}
# Define lifecycle cutpoints
t_cutpoints_long <- t_cutpoints %>%
  #filter(REPORT_LOWERBOUND < as.Date("2018-07-01")) %>%
  filter(REPORT_LOWERBOUND != CLOSE_LOWERBOUND) %>% 
  mutate_at(vars(REPORT_LOWERBOUND:CLOSE_UPPERBOUND), ymd_hms) %>%
  #select(-DECISION_LOWERBOUND, -DECISION_UPPERBOUND) %>% 
  tidyr::gather(-CASE_ID, -CASE_TYPE, -PRODUCT_CODE, key = CUTPOINT, value = CUTDATE) %>%
  arrange(CASE_ID, CUTPOINT) %>% 
  filter(!is.na(CUTDATE))


# Org specific event seqs
t_events_ccc <- t_eventlog %>%
  filter(
        CASE_ID %in% t_cutpoints_long$CASE_ID &
        ACTIVITY_TYPE == "KONTAKT CCC" &
        ACTIVITY_CHANNEL == "CALL") %>%
  select(CASE_ID, CASE_TYPE, EVENT_END)


t_events_okk <- t_eventlog %>%
  filter(
        CASE_ID %in% t_cutpoints_long$CASE_ID &
        ACTIVITY_TYPE == "KONTAKT OKK") %>%
  select(CASE_ID, CASE_TYPE, EVENT_END)

# Define Func to Compute Bins
create_bins_2 <- function(df, case_id) {
  t_cutpoints_long_filtered <- t_cutpoints_long[t_cutpoints_long$CASE_ID == case_id, ] %>% arrange(CUTDATE)
  as.character(cut(df$EVENT_END,
    breaks = c(t_cutpoints_long_filtered$CUTDATE, Inf),
    labels = t_cutpoints_long_filtered$CUTPOINT
  ))
}

# Genereate bins
by_case_id_ccc <- t_events_ccc %>%
  #select(-MILESTONES) %>% 
  group_by(CASE_ID, CASE_TYPE) %>%
  nest() %>%
  mutate(BINS = map2(data, .$CASE_ID, ~create_bins_2(df = .x, case_id = .y)))
```

```{r, message=FALSE}
# Graph
by_case_id_ccc %>% select(CASE_ID, CASE_TYPE, data, BINS) %>% unnest() %>% 
  mutate(
    PERIOD = case_when(
      is.na(BINS) ~ '1_BEFORE_REPORT',
      BINS == 'REPORT_LOWERBOUND' ~ '2_ON_REPORT',
      BINS == 'REPORT_UPPERBOUND' ~ '3_BETWEEN_REPORT_CLOSE',
      BINS == 'CLOSE_LOWERBOUND' ~ '4_ON_CLOSE',
      BINS == 'CLOSE_UPPERBOUND' ~ '5_AFTER_CLOSE'
    )
  ) %>% 
  group_by(PERIOD) %>% 
  summarize(N_OF_CALLS = n()) %>% 
  ungroup() %>% 
  ggplot(aes(x = PERIOD, y = N_OF_CALLS)) +
    geom_bar(stat = "identity") +
    theme(axis.text.x = element_text(angle = 90)) +
    labs(
        x = "Lifecycle",
        y = "# of Calls",
        title = "Number of Calls across Claim File Lifecycle"
      )
```


### 3.1.2. Contact Center Calls across Claims Lifecycle by Process Branch

Most calls are claim report calls on the standard branch. Other branches have very little or no calls.

```{r, message=FALSE}
# Graph
by_case_id_ccc %>% select(CASE_ID, CASE_TYPE, data, BINS) %>% unnest() %>% 
  mutate(
    PERIOD = case_when(
      is.na(BINS) ~ '1_BEFORE_REPORT',
      BINS == 'REPORT_LOWERBOUND' ~ '2_ON_REPORT',
      BINS == 'REPORT_UPPERBOUND' ~ '3_BETWEEN_REPORT_CLOSE',
      BINS == 'CLOSE_LOWERBOUND' ~ '4_ON_CLOSE',
      BINS == 'CLOSE_UPPERBOUND' ~ '5_AFTER_CLOSE'
    )
  ) %>% 
  mutate(CASE_TYPE = factor(CASE_TYPE, levels = c('Simple', 'Standard','Exception'))) %>% 
  group_by(PERIOD, CASE_TYPE) %>% 
  summarize(N_OF_CALLS = n()) %>% 
  ungroup() %>% 
  ggplot(aes(x = PERIOD, y = N_OF_CALLS)) +
    geom_bar(stat = "identity") +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_grid(.~CASE_TYPE) +
    labs(
        x = "Lifecycle",
        y = "# of Calls",
        title = "Number of Calls across Claim File Lifecycle by Process Branch"
      )
```





## 3.2. Claims Handling

### 3.2.1. Claims Handling Interactions across Claims Lifecycle

Claim Handling Center commits most interactions after the first payment.

```{r, message=FALSE}
# Genereate bins
by_case_id_okk <- t_events_okk %>%
  #select(-MILESTONES) %>% 
  group_by(CASE_ID, CASE_TYPE) %>%
  nest() %>%
  mutate(BINS = map2(data, .$CASE_ID, ~create_bins_2(df = .x, case_id = .y)))


# Graph
by_case_id_okk %>% select(CASE_ID, CASE_TYPE, data, BINS) %>% unnest() %>% 
  mutate(
    PERIOD = case_when(
      is.na(BINS) ~ '1_BEFORE_REPORT',
      BINS == 'REPORT_LOWERBOUND' ~ '2_ON_REPORT',
      BINS == 'REPORT_UPPERBOUND' ~ '3_BETWEEN_REPORT_CLOSE',
      BINS == 'CLOSE_LOWERBOUND' ~ '4_ON_CLOSE',
      BINS == 'CLOSE_UPPERBOUND' ~ '5_AFTER_CLOSE'
    )
  ) %>% 
  group_by(PERIOD) %>% 
  summarize(N_OF_CALLS = n()) %>% 
  ungroup() %>% 
  ggplot(aes(x = PERIOD, y = N_OF_CALLS)) +
    geom_bar(stat = "identity") +
    scale_y_continuous(label = unit_format(unit = "K", scale = 1e-3)) +
    theme(axis.text.x = element_text(angle = 90)) +
    labs(
        x = "Lifecycle",
        y = "# of Claims Handling Interactions",
        title = "Number of Claims Handling Interactions across Claim File Lifecycle"
      )
```


### 3.2.2. Claims Handling Interactions across Claims Lifecycle by Process Branch

Most interactions happen on the standard branch after first payment.

```{r, message=FALSE}
# Graph
by_case_id_okk %>% select(CASE_ID, CASE_TYPE, data, BINS) %>% unnest() %>% 
  mutate(
    PERIOD = case_when(
      is.na(BINS) ~ '1_BEFORE_REPORT',
      BINS == 'REPORT_LOWERBOUND' ~ '2_ON_REPORT',
      BINS == 'REPORT_UPPERBOUND' ~ '3_BETWEEN_REPORT_CLOSE',
      BINS == 'CLOSE_LOWERBOUND' ~ '4_ON_CLOSE',
      BINS == 'CLOSE_UPPERBOUND' ~ '5_AFTER_CLOSE'
    )
  ) %>% 
  mutate(CASE_TYPE = factor(CASE_TYPE, levels = c('Simple', 'Standard','Exception'))) %>% 
  group_by(PERIOD, CASE_TYPE) %>% 
  summarize(N_OF_CALLS = n()) %>% 
  ungroup() %>% 
  ggplot(aes(x = PERIOD, y = N_OF_CALLS)) +
    geom_bar(stat = "identity") +
    scale_y_continuous(label = unit_format(unit = "K", scale = 1e-3)) +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_grid(.~CASE_TYPE) +
    labs(
        x = "Lifecycle",
        y = "# of Claims Handling Interactions",
        title = "Number of Claims Handling Interactions across Claim File Lifecycle \nby Process Branch"
      )
```

### 3.2.3. Distribution of Claims Handling Interactions between Report and Close Dates

Most interactions happen after first payment. Breaking down this period by days passed after report shows that:

* most interactions take place 5 to 10 days after first payment

```{r, message=FALSE}
t_events_okk <- t_eventlog %>%
  filter(
    CASE_ID %in% t_cutpoints_long$CASE_ID &
      ACTIVITY_TYPE == "KONTAKT OKK"
  ) %>%
  select(CASE_ID, EVENT_END, USER_ID) %>%
  mutate(DEPT = stringr::str_extract(USER_ID, "[^OKK/].*?(?=\\\\)")) %>%
  mutate(DEPT = case_when(
    DEPT == "Vagyon/Vezeto szakerto" ~ "Home/Experts",
    DEPT == "Logisztikai csoport/Irattaros" ~ "Logistics",
    DEPT == "Logisztikai csoport/Levelfeldolgozo" ~ "Logistics",
    DEPT == "Penzugy" ~ "Financial",
    TRUE ~ "Other"
  ))

t_cutpoints %>%
  select(CASE_ID, CASE_TYPE, CLOSE_UPPERBOUND) %>%
  mutate(
    CASE_TYPE = factor(CASE_TYPE, levels = c('Simple', 'Standard','Exception'))
  ) %>%
  inner_join(t_events_okk, by = "CASE_ID") %>%
  filter(EVENT_END > CLOSE_UPPERBOUND) %>%
  mutate(
    CALL_DIFF = ceiling(as.numeric(difftime(EVENT_END, CLOSE_UPPERBOUND, units = "days"))),
    CALL_DIFF_CAT = cut(CALL_DIFF, c(seq(0, 100, 5), Inf))
  ) %>%
  ggplot(aes(CALL_DIFF)) +
  geom_histogram(bins = 100) +
  coord_cartesian(xlim = c(0, 200)) +
  facet_grid(. ~ CASE_TYPE) +
  labs(
    x = "Days after closing",
    y = "# of Calls",
    title = "Number of Interactions after Claim Closing (First Payment) by Days Passed"
  )
```

Most interactions are committed by the expert team.

```{r, message=FALSE}
t_cutpoints %>%
  select(CASE_ID, CASE_TYPE, CLOSE_UPPERBOUND) %>%
  mutate(
    CASE_TYPE = factor(CASE_TYPE, levels = c('Simple', 'Standard','Exception'))
  ) %>%
  inner_join(t_events_okk, by = "CASE_ID") %>%
  filter(EVENT_END > CLOSE_UPPERBOUND) %>%
  mutate(
    CALL_DIFF = ceiling(as.numeric(difftime(EVENT_END, CLOSE_UPPERBOUND, units = "days"))),
    CALL_DIFF_CAT = cut(CALL_DIFF, c(seq(0, 100, 5), Inf))
  ) %>%
  ggplot(aes(CALL_DIFF)) +
  geom_histogram(bins = 100) +
  coord_cartesian(xlim = c(0, 200)) +
  facet_grid(DEPT ~ CASE_TYPE) +
  labs(
    x = "Days after closing",
    y = "# of Calls",
    title = "Number of Interactions after Claim Closing (First Payment) by Days Passed"
  )
```

***

